---
title: "Final Model and Ensemble - Group 12 - Machine Learning"
output: pdf_document
---


Importing in Packages and reading in the data

```{r}

#importing Packages
library("nnet")
library("data.table")
library("glmnet")
library("caret")
library("rpart")



# logloss function
LogLoss<-function(actual, predicted)
{
  result<- -1/length(actual)*(sum((actual*log(predicted)+(1-actual)*log(1-predicted))))
  return(result)
}


df <- fread('ProjectTrainingData.csv')

```


cleaning the training dataset
```{r}



train_data = df

train_data = subset(train_data, select = -c(hour))

# train_data$date=floor(train_data$hour/100)-141020
# train_data$hour=train_data$hour-14102000-train_data$date*100

train_data[!(C1 %in% c(1005,1002,1010)),C1:=0]
train_data[!(banner_pos %in% c(0,1)),banner_pos:=999]
train_data[!(site_id %in% c("85f751fd","1fbe01fe","e151e245")),site_id:="0"]
train_data[!(site_domain %in% c("c4e18dd6","f3845767","7e091613","7687a86e")),site_domain:="0"]
train_data[!(site_category %in% c("50e219e0","f028772b","28905ebd","3e814130")),site_category:="0"]
train_data[!(app_id %in% c("ecad2386")),app_id:="0"]
train_data[!(app_domain %in% c("7801e8d9","2347f47a","ae637522")),app_domain:="0"]
train_data[!(app_category %in% c("07d7df22","0f2161f8","cef3e649","8ded1f7a")),app_category:="0"]
train_data[!(device_id %in% c("a99f214a")),device_id:="0"]
train_data[!(device_model %in% c("8a4875bd","d787e91b","1f0bc64f")),device_model:="0"]
train_data[!(C15 %in% c(320,300,216,728)),C15:=0]
train_data[!(C16 %in% c(50,250,36)),C16:=0]
train_data[!(C17 %in% c(1722)),C17:=0]
train_data[!(C19 %in% c(35,39,167,47)),C19:=0]
train_data[!(C20 %in% c(-1,100084)),C20:=0]
train_data[!(C21 %in% c(23,79,221)),C21:=0]
train_data=train_data[,-c("device_ip","C14")]


```





Creating a random sample
```{r}

#random sample function
randomSample = function(df,n) { 
  return (df[sample(nrow(df), n),])
}

#creating a random sample 
set.seed(99)
trainsample = randomSample(train_data, 1000000)
# View(head(trainsample))
trainsample = subset(trainsample, select = -c(id))


```

removing redundant features (based on iterative running of models) and converting variables to factors

```{r}

# removing redundant columns
trainsample[(site_domain %in% c("f3845767")),site_domain:="0"]
trainsample[(app_id %in% c("f3845767")),app_id:="1"]


#converting variables into factors
# trainsample$date = as.factor(trainsample$date)
# trainsample$hour = as.factor(trainsample$hour)

trainsample$C1 = as.factor(trainsample$C1)
trainsample$banner_pos = as.factor(trainsample$banner_pos)
trainsample$site_id = as.factor(trainsample$site_id)
trainsample$site_domain = as.factor(trainsample$site_domain)
trainsample$site_category = as.factor(trainsample$site_category)
trainsample$app_domain = as.factor(trainsample$app_domain)
trainsample$site_category = as.factor(trainsample$site_category)

# trainsample$app_id = as.factor(trainsample$app_id)

trainsample$app_domain = as.factor(trainsample$app_domain)
trainsample$app_category = as.factor(trainsample$app_category)
trainsample$device_id = as.factor(trainsample$device_id)
trainsample$device_model = as.factor(trainsample$device_model)
trainsample$device_type = as.factor(trainsample$device_type)
trainsample$device_conn_type = as.factor(trainsample$device_conn_type)
trainsample$C15 = as.factor(trainsample$C15)
trainsample$C16 = as.factor(trainsample$C16)
trainsample$C17 = as.factor(trainsample$C17)
trainsample$C18 = as.factor(trainsample$C18)
trainsample$C19 = as.factor(trainsample$C19)
trainsample$C20 = as.factor(trainsample$C20)
trainsample$C21 = as.factor(trainsample$C21)


```


Creating Training and validation datasets

```{r}


#creating training and validation sets
TrainInd <- ceiling(nrow(trainsample)*0.6)
TrainData <- trainsample[1:TrainInd,]
ValData <- trainsample[(TrainInd+1):nrow(trainsample),]




```


Model 1 : Logistic Regression and predicting the results

```{r}

#running logistic Regression
logit = glm(click ~ . , family=binomial(link='logit'), data = TrainData)

# summary(model)
# logLik(model)
# AIC(model)

#predicting the results
pred_val_logit = predict(logit , newdata = ValData, type = "response")
pred_train_logit = predict(logit , newdata = TrainData, type = "response")


```




Computing the Log Loss for Logistic Regression using the Validation datasets

```{r}

print("Log Loss for Logistic Regression")

val_loss_logit = LogLoss(actual=ValData$click, predicted=pred_val_logit)

print(val_loss_logit)
```

Ensembling

Including the predicted results for logistic Regression into the training dataset and Training a decision tree on it. This will enable us to capitalize on both models.

Model 2 : Training a decision Tree Model with the logistic Regression results included




```{r}

#including the logistic regression results

TrainData2 = TrainData
pred_train_logit = as.data.frame(pred_train_logit)
TrainData2$pred_logit = pred_train_logit$pred_train_logit


ValData2 = ValData
pred_val_logit = as.data.frame(pred_val_logit)
ValData2$pred_logit = pred_val_logit$pred_val_logit


```



Using the training set logistic regression probabilities in the decision tree training



```{r}

TrainData2$click = as.factor(TrainData2$click)


# library("rpart")
rpc <- rpart.control(minsplit=20,maxdepth=20,cp=0)
ens_dtree <- rpart(click ~ .,data=TrainData2,control=rpc)

# Find the cp parameter for the best model and prune the tree.
bestcp <- ens_dtree$cptable[which.min(ens_dtree$cptable[,"xerror"]),"CP"]

# Store the "best" model in out1
ens_dtree2 <- prune(ens_dtree,cp=bestcp)
```

Predicting results

```{r}

pred_val_ens_dtree <- predict(ens_dtree2,newdata=ValData2,type="prob")
pred_train_ens_dtree <- predict(ens_dtree2,newdata=TrainData2,type="prob")

```


Getting the log loss for the ensemble on the validation dataset
```{r}

pred_val_ens_dtree = as.data.frame(pred_val_ens_dtree)


# ValData$click = as.numeric(ValData$click)
val_loss_ens_dtree = LogLoss(actual= ValData$click, predicted = pred_val_ens_dtree$`1`)

print("Log Loss for Ensemble Decision Tree")

print(val_loss_ens_dtree)

```


Evaluating the test dataset

Creating a prediction function for the test dataset


Reading in the test dataset and reducing features

```{r}
# TestData <- fread('ProjectTestData.csv')
# # dt_trainsample <- fread('trainsample.csv')
# # TestData = 0
# 
# test_data = TestData
# TestData = 0
# test_data = subset(test_data, select = -c(hour))
# 
# 
# # TestData$date=floor(TestData$hour/100)-141020
# # test_data$hour=test_data$hour-14102000-test_data$date*100
# 
# test_data[!(C1 %in% c(1005,1002,1010)),C1:=0]
# test_data[!(banner_pos %in% c(0,1)),banner_pos:=999]
# test_data[!(site_id %in% c("85f751fd","1fbe01fe","e151e245")),site_id:="0"]
# test_data[!(site_domain %in% c("c4e18dd6","f3845767","7e091613","7687a86e")),site_domain:="0"]
# test_data[!(site_category %in% c("50e219e0","f028772b","28905ebd","3e814130")),site_category:="0"]
# test_data[!(app_id %in% c("ecad2386")),app_id:="0"]
# test_data[!(app_domain %in% c("7801e8d9","2347f47a","ae637522")),app_domain:="0"]
# test_data[!(app_category %in% c("07d7df22","0f2161f8","cef3e649","8ded1f7a")),app_category:="0"]
# test_data[!(device_id %in% c("a99f214a")),device_id:="0"]
# test_data[!(device_model %in% c("8a4875bd","d787e91b","1f0bc64f")),device_model:="0"]
# test_data[!(C15 %in% c(320,300,216,728)),C15:=0]
# test_data[!(C16 %in% c(50,250,36)),C16:=0]
# test_data[!(C17 %in% c(1722)),C17:=0]
# test_data[!(C19 %in% c(35,39,167,47)),C19:=0]
# test_data[!(C20 %in% c(-1,100084)),C20:=0]
# test_data[!(C21 %in% c(23,79,221)),C21:=0]
# test_data=test_data[,-c("device_ip","C14")]
# 
# 
# # removing redundant columns
# test_data[(site_domain %in% c("f3845767")),site_domain:="0"]
# test_data[(app_id %in% c("f3845767")),app_id:="1"]
# 
# 
# # fwrite(test_data, 'test_short.csv')

```


Factorizing the test dataset and removing further columns

```{r}



#converting variables into factors
# test_data$date = as.factor(test_data$date)
# test_data$hour = as.factor(test_data$hour)

# test_data$C1 = as.factor(test_data$C1)
# test_data$banner_pos = as.factor(test_data$banner_pos)
# test_data$site_id = as.factor(test_data$site_id)
# test_data$site_domain = as.factor(test_data$site_domain)
# test_data$site_category = as.factor(test_data$site_category)
# test_data$app_domain = as.factor(test_data$app_domain)
# test_data$site_category = as.factor(test_data$site_category)

# test_data$app_id = as.factor(test_data$app_id)
# 
# test_data$app_domain = as.factor(test_data$app_domain)
# test_data$app_category = as.factor(test_data$app_category)
# test_data$device_id = as.factor(test_data$device_id)
# test_data$device_model = as.factor(test_data$device_model)
# test_data$device_type = as.factor(test_data$device_type)
# test_data$device_conn_type = as.factor(test_data$device_conn_type)
# test_data$C15 = as.factor(test_data$C15)
# test_data$C16 = as.factor(test_data$C16)
# test_data$C17 = as.factor(test_data$C17)
# test_data$C18 = as.factor(test_data$C18)
# test_data$C19 = as.factor(test_data$C19)
# test_data$C20 = as.factor(test_data$C20)
# test_data$C21 = as.factor(test_data$C21)






```


predicting results for logistic regression and appending them to a test dataset copy

```{r}
# 
# test_data2 = as.data.table(test_data)
# 
# test_data2$pred = predict(logit , newdata = test_data, type = 'response')
# 
# 
# pred_ens = as.dataframe(pred_test_logit)
# 
# test_df = 



```


